Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-04-02 PandaEvolution.tex
PanDA Broker Architecture and anonymization
Add caption

\begin{figure}
  \begin{center}
    \includegraphics[width=\columnwidth]{figures/PanDA_setup_at_OLCF.png}
    \caption{Schematic view of the PanDA Broker.}
  \end{center}
\label{fig:panda_broker}
\end{figure}

>>>>

\begin{figure}
  \begin{center}
    \includegraphics[width=\columnwidth]{figures/panda_broker_architecture.pdf}
    \caption{PanDA Broker architecture as deployed on Titan. Numbers indicates
    the execution process of a detector simulation job, part of the production
    ATLAS MD workflow.}
  \end{center}
\label{fig:panda_broker}
\end{figure}
